### 2024-02-18 documentation/thesis/thesis_document.tex
.

The electronics consist of the magnetic field sensor and the electrical
interface to connect it to a \gls{pc} in the form of a microcontroller.

The focus is on utilising existing microcontroller development and
evaluation boards, which already integrate all the components required
for basic operation. This not only enabled a time-saving implementation,
but also ensured a cost-efficient realisation. A \emph{Raspberry Pi
Pico} and a \emph{STM32F4} are used as a computer-sensor interface for
this thesis, which are popular, cost-effective and simple to implement.

@@

The \emph{MRPReading} module performs an essential role in streamlining
the centralized management of measurement data. It serves as a storage
provider for various measurements, offering functionalities that
facilitate the creation and addition of data records. To customise and
add meta-data, users have the flexibility to configure parameters
through the dedicated \emph{MRPMeasurementConfig} module into an
\emph{MRPReading} instance.

@@

A crucial point is the management of the meta data, which further
describes the measurement. This is realised in the example using the
\emph{set\_additional\_data} function. Finally, the measurement is
exported for archiving and further processing; various export formats
are available. Using the \emph{dump\_to\_file} function, the measurement
can be converted into an open \gls{json} format.

>>>>

The electronics consist of the magnetic field sensor and the electrical
interface to connect it to a \gls{pc} in the form of a microcontroller.
The focus is on utilising existing microcontroller development and
evaluation boards, which already integrate all the components required
for basic operation. This not only enabled a time-saving implementation,
but also ensured a cost-efficient realisation. A \emph{Raspberry Pi
Pico} and a \emph{STM32F4} are used as a computer-sensor interface for
this thesis, which are popular, cost-effective and simple to implement.

@@

The \emph{MRPReading} module performs an essential role in streamlining
the centralized management of measurement data. It serves as a storage
provider for various measurements, offering functionalities that
facilitate the creation and addition of data records. To customise and
add meta-data, users have the flexibility to configure parameters
through the dedicated \emph{MRPMeasurementConfig} module into a
\emph{MRPReading} instance.

@@

A crucial point is the management of the meta data, which further
describes the measurement. This is realised in the example using the
\emph{set\_additional\_data} function. Finally, the measurement is
exported for archiving and further processing; various export formats
are available. Using the \emph{dump\_to\_file} function, the measurement
can be converted into a open \gls{json} format.
